Consistent Polyhedral Surrogates via Embedding

### 2019-05-19 notes/jessie-proof-sketches.tex
Redid proof of prop 1

  For the forward implication, suppose $L$ embeds the discrete loss $\ell$.
  Then $\Gamma := \prop{L}$ embeds the finite property $\gamma$ elicited by $\ell$.

  Generating $\R := \{u_f\}_{f\in F}$, we know that $\gamma = \phi(\Gamma \cap \R)$, where the two are the same up to relabeling \jessie{need more thorough argument on this?  Not sure if I believe it...} and $\Gamma \cap \R$ is elicited by $L|_\R$ by \jessie{COLT Lemma 11}, and thus has the same Bayes Risk as $L|_\R$ by \jessie{cite FK General Truthfulness Theorem 2}.
  Applying \jessie{COLT Lemma 11}, we then observe that $\risk{L} = \risk{L|_\R} = \risk{\ell}$.

@@

  For the reverse implication, we use contradiction. \jessie{But no properties... I didn't see how.  Different technique from below though.}

  \jessie{TODO: If we use this, change notation of $P_\ell$ to match what's already in the paper}
  First, assume that $\risk{\ell} \neq \risk{L} +c$ for any constant $c$.
  Denote by $P_\ell$ the facets of $\risk{\ell}$ projected onto $\simplex$, which must be different than the facets of $\risk{L}$ projected onto $\simplex$, denoted $P_L$.
  That means, for some $p \in \simplex$ on the interior of a cell in $P_\ell$, we know $\nabla \risk{\ell}(p) \neq \nabla \risk{L}(p)$ \raf{don't see why this is necessarily true}.
  Therefore, we know the argmins of $L$ and $\ell$ are unique and as the subgradients of the risks are not equal, then $r \in \argmin_{r'} \ell(r,p) \implies \varphi(r) \not \in \argmin_u L(u,p)$, and thus we contradict our embedding assumption.

  Now, if $\risk{\ell} = \risk{L}+c$ for some constant $c \neq 0$, then we contradict part $(i)$ of the definition of embedding where the loss values must match up.

  Therefore, if the loss $L$ embeds the discrete loss $\ell$, then we must observe $\risk{L} = \risk{\ell}$.
\end{proof}
\hrulefill
\begin{proof}[Non-property version]
  \raf{Use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
  %Jessie's first attempt at a proof
  First, suppose $L$ embeds $\ell$, and fix $p \in \simplex$.
  We want to show for all $p \in \simplex$ that $\inf_{u\in\reals^d} L(u,p) = \min_{r \in \R} \ell(r, p)$.
  Consider two cases: first suppose there exists a $u \in \reals^d$ so that $u \in \arginf_{u' \in \reals^d}L(u',p)$ and $u \in \varphi(\R)$.
  Then
  \begin{align*}
  \inf_u L(u,p) = \min_{r \in \R} L(\varphi(r), p) = \min_{r \in \R} \ell(r, p)
  \end{align*}
   first by the case assumption and then by the definition of embedding.
  Now in the second case, if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
  Therefore, $r \in \argmin_r' \ell(r', p) \not\implies \varphi(r) \in \argmin_u L(u,p)$ contradicts the assertion that $L$ embeds $\ell$.

>>>>

  \jessie{Redone.  Original version in comments below.}
  For the forward implication, suppose $L$ embeds the discrete loss $\ell$ via the embedding $\varphi$.
  Then $\Gamma := \prop{L}$ embeds the finite property $\gamma:\simplex \toto \R$ elicited by $\ell$.
  Call $\R' := \varphi(\R)$.
  For all $p \in \simplex$, we know that $\Gamma(p) = \varphi(\gamma(p))$.
  We know $\gamma' := \Gamma(p) \cap \R'$ is nonempty for all $p \in \simplex$ since $\Gamma(p) = \varphi(\gamma(p)) \in \R'$.
  By \jessie{COLT Lemma 11}, we know that $L|_{\R'}$ elicits $\gamma'$ and $\risk{L} = \risk{L|_{\R'}}$.

%  As $|\R| = |\R'|$, we know there is a bijection from one to the other defined by the embedding $\varphi$ on a restricted domain.
  By embedding, the loss values $L(\varphi(r)) = \ell(r)$ for all $r \in \R$, and so the expected values $\inprod{p}{L(\varphi(r))} = \inprod{p}{\ell(r)}$ for all $p \in \simplex$ and $r \in \R$.
  In particular, $\min_{u \in \R'}\inprod{p}{L(u)} = \min_{r \in \R}\inprod{p}{\ell(r)}$ for all $p \in \simplex$. 
  Therefore, we can conclude that $\risk{L|_{\R'}} = \risk{\ell}$.
  Combining with the above statement, we conclude $\risk{L} = \risk{\ell}$.

%  Generating $\R := \{u_f\}_{f\in F}$, we know that $\gamma = \phi(\Gamma \cap \R)$, where the two are the same up to relabeling \jessie{need more thorough argument on this?  Not sure if I believe it...} and $\Gamma \cap \R$ is elicited by $L|_\R$ by \jessie{COLT Lemma 11}, and thus has the same Bayes Risk as $L|_\R$ by \jessie{cite FK General Truthfulness Theorem 2}.
%  Applying \jessie{COLT Lemma 11}, we then observe that $\risk{L} = \risk{L|_\R} = \risk{\ell}$.

@@

  To start, assume that $\risk{L} = \risk{\ell}$.
  The projection of the epigraphs onto $\simplex$ must then form the same power diagram \jessie{COLT Theorem 33}, corresponding to the level sets of the properties each loss elicits.
  Notably, \jessie{as in proof of COLT Prop 12,} the facets of $\risk{\ell}$ project onto the level sets of $\gamma := \prop{\ell}$.
  As $\ell$ is discrete, we know $\gamma$ is finite, and so the level sets of $\gamma$ are full-dimensional \jessie{by COLT Lemma 10} and union to the simplex by nondegeneracy of $\gamma$.
  Since the risks of $L$ and $L$ are the same (and therefore, so are their projections onto $\simplex$), this same [finite] subset $\Theta$ of the level sets of $\Gamma$ that union to the simplex and are full-dimensional.
  By \jessie{COLT Prop 12}, we can then conclude that $\Gamma$ embeds the finite property $\gamma$, and thus $L$ embeds the discrete loss $\ell$.

%  \jessie{TODO: If we use this, change notation of $P_\ell$ to match what's already in the paper}
%  First, assume that $\risk{\ell} \neq \risk{L} +c$ for any constant $c$.
%  Denote by $P_\ell$ the facets of $\risk{\ell}$ projected onto $\simplex$, which must be different than the facets of $\risk{L}$ projected onto $\simplex$, denoted $P_L$.
%  That means, for some $p \in \simplex$ on the interior of a cell in $P_\ell$, we know $\nabla \risk{\ell}(p) \neq \nabla \risk{L}(p)$ \raf{don't see why this is necessarily true}.
%  Therefore, we know the argmins of $L$ and $\ell$ are unique and as the subgradients of the risks are not equal, then $r \in \argmin_{r'} \ell(r,p) \implies \varphi(r) \not \in \argmin_u L(u,p)$, and thus we contradict our embedding assumption.
%  
%  Now, if $\risk{\ell} = \risk{L}+c$ for some constant $c \neq 0$, then we contradict part $(i)$ of the definition of embedding where the loss values must match up.
%  
%  Therefore, if the loss $L$ embeds the discrete loss $\ell$, then we must observe $\risk{L} = \risk{\ell}$.
\end{proof}
\hrulefill
\begin{proof}[Non-property version]
  \raf{Use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
  %Jessie's first attempt at a proof
  First, suppose $L$ embeds $\ell$, and fix $p \in \simplex$.
  We want to show for all $p \in \simplex$ that $\inf_{u\in\reals^d} L(u,p) = \min_{r \in \R} \ell(r, p)$.
  Consider two cases: first suppose there exists a $u \in \reals^d$ so that $u \in \arginf_{u' \in \reals^d}L(u',p)$ and $u \in \varphi(\R)$.
  Then
  \begin{align*}
  \inf_u L(u,p) = \min_{r \in \R} L(\varphi(r), p) = \min_{r \in \R} \ell(r, p)
  \end{align*}
   first by the case assumption and then by the definition of embedding.
  Now in the second case, if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
  Therefore, $r \in \argmin_r' \ell(r', p) \not\implies \varphi(r) \in \argmin_u L(u,p)$ contradicts the assertion that $L$ embeds $\ell$.
